Basic regression in Gaussian processes

### 2019-10-30 notebook/gp-manual-vs-greta.Rmd
Exporing the "two fold path" in GPs
Now that Nick has set me straight here on the differences!

@@

@@

```{r}
# fit the model by Hamiltonian Monte Carlo
m <- model(f_plot, rbf_len, rbf_var, obs_sd)
draws <- mcmc(m, chains = 1, one_by_one = TRUE)
```

```{r}
df <- draws[[1]] %>% as_tibble(.name_repair = "universal") 
hyperpars <- df %>% dplyr::select(rbf_len, obs_sd, rbf_var)  
posterior <- df %>% dplyr::select(-rbf_len, -obs_sd, -rbf_var)

hyperpars %>% colMeans()
#hyperpars %>% gather() %>% ggplot(aes(x = value, fill=key)) + stat_density() + facet_wrap(~key)
```

```{r}
posterior %>% t() %>% as_tibble() %>% dplyr::select(1:200) %>% mutate(x = x_predict) %>% pivot_longer(-x)  %>%
  ggplot(aes(x,value)) + 
  geom_line(aes(group=name), alpha=0.3, col=rgb(0.7, 0.1, 0.4, 0.1)) +
  geom_point(data = obs, aes(x,y))
```

>>>>

```{r}
# kernel & GP
y <- t(obs$y)
x <- obs$x

@@

n <- length(x)
## More explicit
distribution(y) <- multivariate_normal(zeros(1, n), kernel(x, x) + diag(n) * obs_sd)

## This is more generic, we could have any function here.  Most methods assume additive Gaussian
## noise to be able to exploit analytical sampling of the GP
#distribution(y)<- normal(f, obs_sd)

@@

```{r}
# fit the model by Hamiltonian Monte Carlo over hyperparameters only, not sampling from the GP
m <- model(rbf_len, rbf_var, obs_sd)
draws <- mcmc(m, chains = 1, one_by_one = TRUE)
```

```{r}
df <- draws[[1]] %>% as_tibble(.name_repair = "universal") 
hyperpars <- df %>% dplyr::select(rbf_len, obs_sd, rbf_var)  
#posterior <- df %>% dplyr::select(-rbf_len, -obs_sd, -rbf_var)

posterior_means <- hyperpars %>% colMeans()
posterior_means
hyperpars %>% gather() %>% ggplot(aes(x = value, fill=key)) + stat_density() + facet_wrap(~key)
```

And wow, we can do this math in greta...

```{r}
cov <- kernel
sigma.n <- posterior_means["obs_sd"]
cov_xx_inv <- solve(cov(obs$x, obs$x) + sigma.n^2 * diag(1, length(obs$x)))
Ef <- cov(x_predict, obs$x) %*% cov_xx_inv %*% greta_array(obs$y)
Cf <- cov(x_predict, x_predict) - cov(x_predict, obs$x)  %*% cov_xx_inv %*% cov(obs$x, x_predict)
```

```{r}
#posterior %>% t() %>% as_tibble() %>% dplyr::select(1:200) %>% mutate(x = x_predict) %>% pivot_longer(-x)  %>%
#  ggplot(aes(x,value)) + 
#  geom_line(aes(group=name), alpha=0.3, col=rgb(0.7, 0.1, 0.4, 0.1)) +
#  geom_point(data = obs, aes(x,y))
```
